Sociology of Education Association Proposal

### 2020-10-30 sea_conference/soc_of_ed_proposal.Rmd
moved soc of ed to a sub-directory

---
title: "Sociology of Education Association Proposal"
output:
  bookdown::pdf_document2:
    toc: false
    number_sections: false
bibliography: ./other/burd_recruiting_chapter.bib
csl: ./other/apa.csl
urlcolor: blue
header-includes:
  - \usepackage{pdflscape}
  - \usepackage{geometry}
---

@@

ozanj@ucla.edu
\end{center}

@@

@@

```{r, ego-table-privu, echo = FALSE}
df <- readRDS('./assets/tables/table_ego.RDS')
knitr::kable(
  df %>% select(-Characteristics), row.names = F, # select(-ID, -Characteristics)
  caption = 'Characteristics of private high schools visited by each private college and university') %>% landscape(margin = NULL) %>%
  kable_styling(latex_options = 'scale_down')
```

```{r, hs-print-privu, echo = FALSE}
df <- readRDS('./assets/tables/table_2mode.RDS') %>% head(n=20)

@@

```{r, hs-table-privu-agg, echo = FALSE}
df <- readRDS('./assets/tables/table_2mode_agg.RDS')

@@

```{r two-mode-plot, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "2-mode network plot consisting of visits by public and private colleges and universities to private high schools"}
knitr::include_graphics('assets/figures/plot_g_2mode.pdf')
#https://stackoverflow.com/questions/15625990/how-to-set-size-for-local-image-using-knitr-for-markdown
```

```{r two-mode-plot-privu, fig.align = 'center', echo = FALSE, out.width = "75%", fig.cap = "2-mode network plot consisting of visits by private colleges and universities to private high schools"}
knitr::include_graphics('assets/figures/plot_g_2mode_privu.pdf')
```

>>>>

---
title: "Sociology of Education Association Proposal"
output:
  bookdown::pdf_document2:
    toc: false
    number_sections: false
bibliography: ./../other/burd_recruiting_chapter.bib
csl: ./../other/apa.csl
urlcolor: blue
header-includes:
  - \usepackage{pdflscape}
  - \usepackage{geometry}
---

@@

ozanj@ucla.edu

!!!!!!!!!!!CRYSTAL ADD YOUR CONTACT INFO HERE!!!!!!!!!!!
\end{center}

@@

# Overview

This paper analyzes off-campus recruiting visits to U.S. private high schools made by a sample of public research universities and sample of selective private colleges and universities in 2017.

We utilize social network methods and emphasize comparisons within and between public and private postsecondary institutions. Analyses are informed by two broad, related questions. First, which types of private high schools receive visits from which types of colleges and universities? Second, to what do extent colleges and universities visit private high schools that share similar characteristics with the college (e.g., geographic region, religious affiliation, academic reputation, and racial composition)?

This chapter analyzes off-campus recruiting visits by a sample of public research universities and a sample of selective private colleges and universities in 2017. We collected visit data by "scraping" URLs (e.g., "Coming to a neighborhood near you") once per week from college/university admissions websites and -- for the sample of public research universities -- by issuring public records requests.

this chapter analyzes off-campus visits to private high schools by public research universities and by selective private colleges and universities.

The motivation for comparing the behavior of public and private coleges/universities is based on the idea that (out-of-state) visits to private high schools are antithetical to the stated mission of public research universities. By contrast, recruiting visits to private high schools are consistent with the mission of private colleges and universities. From this perspective, out-of-state visits to private schools by public research universities is one example of "privatization." A weakness of the privatization literature is that few empirical studies compare the public and private institutions with respect to particular behaviors associated with privatization [@RN4543]. Therefore, by comparing the (mostly out-of-state) visits to private high schools by public research universities to those of private colleges and universities, we hope to develop new insights about the privatization of public higher education.

# Literature review and theory

# Data and methods

# Findings

# Significance

@@

```{r, ego-table-privu, echo = FALSE}
df <- readRDS('./../assets/tables/table_ego.RDS')
knitr::kable(
  df %>% select(-Characteristics), row.names = F, # select(-ID, -Characteristics)
  caption = 'Characteristics of private high schools visited by each private college and university') %>% landscape(margin = NULL) %>%
  kable_styling(latex_options = 'scale_down')
```

```{r, hs-print-privu, echo = FALSE}
df <- readRDS('./../assets/tables/table_2mode.RDS') %>% head(n=20)

@@

```{r, hs-table-privu-agg, echo = FALSE}
df <- readRDS('./../assets/tables/table_2mode_agg.RDS')

@@

```{r two-mode-plot, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "2-mode network plot consisting of visits by public and private colleges and universities to private high schools"}
knitr::include_graphics('./../assets/figures/plot_g_2mode.pdf')
#https://stackoverflow.com/questions/15625990/how-to-set-size-for-local-image-using-knitr-for-markdown
```

```{r two-mode-plot-privu, fig.align = 'center', echo = FALSE, out.width = "75%", fig.cap = "2-mode network plot consisting of visits by private colleges and universities to private high schools"}
knitr::include_graphics('./../assets/figures/plot_g_2mode_privu.pdf')
```
